### 2019-08-01 paper.tex
Full paper on thesis

\section*{TraMoS V: Updated ephemeris and transit timing variations of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab}

\chapterauthor{P\'ia Cort\'es-Zuleta, Patricio Rojo, Songhu Wang, Tobias C. Hinse, Sergio Hpyer, Bastian Sanhueza, Patricio Correa-Amaro, Julio Albornoz}

>>>>

\section*{TraMoS V: Updated ephemeris and transit timing variations of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab\footnote{Copy of paper submitted to A\&A on July 9, 2019.}}

\chapterauthor{P\'ia Cort\'es-Zuleta, Patricio Rojo, Songhu Wang, Tobias C. Hinse, Sergio Hoyer, Bastian Sanhueza, Patricio Correa-Amaro, Julio Albornoz}
